{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2018-01-17 wacv_for_review.tex
revision.

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E_h = \min_{\boldsymbol{h}}\frac{1}{2}||\boldsymbol{y}-\sum_{c=1}^{C}\boldsymbol{h_{c}}*\boldsymbol{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\boldsymbol{h_{c}}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where we seek for $\boldsymbol{h}$ that minimizes $E$ given the desired
continuous response, $\boldsymbol{y}$, and the training template
$\boldsymbol{x}$.  The parameter $c$ enables one to integrate features in
the form of multiple channels, such as HoG and color, in this setup
\cite{henriques2015high,galoogahi2013multi}.  A closed-form solution
for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
closed-form solution, an element-wise multiplication in frequency
domain was proposed to learn the frequency domain correspondence of
$\boldsymbol{h}$, $\boldsymbol{\hat{w}}$:
\begin{equation}
\boldsymbol{\hat{w}} = \boldsymbol{\hat{x}^{*}}*\boldsymbol{\hat{y}}(\boldsymbol{\hat{x}^{*}}*\boldsymbol{\hat{x}}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of $\boldsymbol{\hat{w}}$, $\boldsymbol{\hat{\alpha}}$ , is proposed to increase robustness
to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized non-linear Fourier
domain dual form solution is expressed as
\begin{equation}
\boldsymbol{\hat{\alpha}} = \boldsymbol{\hat{y}}(\boldsymbol{\hat{k}^{xx^{'}}}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\lambda$ represents the regularization weight whereas $\boldsymbol{\hat{k}^{xx^{'}}}$ denotes
 the first row of the kernel matrix $\boldsymbol{K}$ known as \textit{gram matrix} and is expressed as
\begin{equation}
\boldsymbol{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\boldsymbol{x}||^{2}+||\boldsymbol{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\boldsymbol{\hat{x}_{c}}^{*}\odot \boldsymbol{\hat{x}_{c}}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $\boldsymbol{w}$ and integrating
multi-channel features such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}.
In the detection phase, the learned correlation filter is correlated
with the first row of the gram matrix, $\boldsymbol{k^{xz^{'}}}$, which
contains the similarity values between the learned feature template
$\boldsymbol{x}$ and the new test template $\boldsymbol{z}$. This can be
formulated as
\begin{equation}
\boldsymbol{r(z)} = F^{-1}(\boldsymbol{\hat{k}^{xz^{'}}} \odot \boldsymbol{\hat{\alpha}})
\end{equation}
where $\boldsymbol{r}$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features in tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activation of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to increased translational invariance in this
layer. \cite{ma2015hierarchical} proposed a KCF tracker integrating
features with higher abstraction capacity.  Their method first employs
the third convolutional layer features to estimate the response
map. In the next stage, the KCF, concentrating on the second
convolutional layer features, is run to update transition. The third
KCF then works on the transition given by the previous KCF and learns
the first convolutional layer features to update the transition. This
coarse-to-fine translation estimation approach accommodates different levels of abstractions
of the object. However, it runs multiple KCFs in a sequential fashion,
increasing the run-time complexity. For this reason, we follow an
approach similar to \cite{danelljan2015convolutional}, in order to
embed deep features in {\it E}nKCF. Our {\it E}nKCF algorithm enables
us to exploit different level of feature encodings with different
KCFs. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider
at least twice bigger area than the scale filter, $R_{s}$. Given this,
we can assign deeper feature encodings to $R_{s}$ as it learns less
spatial information than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign
the activation of the fourth convolutional layer features
($26\times26\times128$) to $R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$
are assigned the activation of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. The conv222 setting stands for the assignment of
the activation of $2^{th}$ convolutional layer features of VGGNet to
$R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet since it
provides higher spatial resolution at the first several layers than
AlexNet \cite{krizhevsky2012imagenet}.

@@

\textbf{Particle Filter for Smoothing Transition among KCFs} As
explained earlier, the {\it E}nKCF updates the target's scale at every
other $k$ frames. Although the strategy of updating every other $k$th
frames will result in an optimal run-time performance, this may lead
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs. In particular, we use a
particle filter to estimate the target's image coordinate based on the
{\it E}nKCF's outputs. The state in this paper, $\boldsymbol{X_{t}}$,
represents the target's pixel coordinates and its velocity,
$\boldsymbol{X_{t}} = \lbrace x, y, v_{x}, v_{y} \rbrace$, where $x$ and
$y$ are the pixel coordinates of the target's centroid, $v_x$ and
$v_y$ are the velocities estimated along the $x$-axis and
$y$-axis. The particle filter predicts, using a constant velocity
motion model, the target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update its state. The particle weight is computed
as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M}
\boldsymbol{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ denotes the weight of
the particle $p$ at time $t$, and $N$ and $M$ denote the number of
rows and columns of the confidence map.

@@

\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.60cm]{./figures/pr_deep.eps}
\includegraphics[width=3.70cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it fHoG} + {\it color-naming}) 
performance with Deep{\it E}nKCF on the UAV123
dataset. The runtime performance the Deep{\it E}nKCF (conv224) is 30.74 fps 
whereas the conv222 setting yields to a 35.23 fps tracker on a CPU. }
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

>>>>

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E_h = \min_{\boldsymbol{h}}\frac{1}{2}||\boldsymbol{y}-\sum_{c=1}^{C}\boldsymbol{h_{c}}*\boldsymbol{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\boldsymbol{h_{c}}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where we seek for $\boldsymbol{h}$ that minimizes $E$ given the desired
continuous response, $\boldsymbol{y}$, and the training template
$\boldsymbol{x}$.  The parameter $c$ enables one to integrate features in
the form of multiple channels, such as HoG and color, in this setup
\cite{henriques2015high,galoogahi2013multi}.  A closed-form solution
for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
closed-form solution, an element-wise multiplication in frequency
domain was proposed to learn the frequency domain correspondence of
$\boldsymbol{h}$, $\boldsymbol{\hat{w}}$:
\begin{equation}
\boldsymbol{\hat{w}} = \boldsymbol{\hat{x}^{*}}*\boldsymbol{\hat{y}}(\boldsymbol{\hat{x}^{*}}*\boldsymbol{\hat{x}}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
Where $*$ is an element-wise multiplication. A non-linear version of
$\boldsymbol{\hat{w}}$ and $\boldsymbol{\hat{\alpha}}$ are proposed to
increase robustness to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized non-linear
Fourier domain dual form solution is expressed as
\begin{equation}
\boldsymbol{\hat{\alpha}} = \boldsymbol{\hat{y}}(\boldsymbol{\hat{k}^{xx^{'}}}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\lambda$ represents the regularization weight whereas $\boldsymbol{\hat{k}^{xx^{'}}}$ denotes
 the first row of the kernel matrix $\boldsymbol{K}$ known as \textit{gram matrix} and is expressed as
\begin{equation}
\boldsymbol{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\boldsymbol{x}||^{2}+||\boldsymbol{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\boldsymbol{\hat{x}_{c}}^{*}\odot \boldsymbol{\hat{x}_{c}}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $\boldsymbol{w}$ and integrating
multi-channel features such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}.
In the detection phase, the learned correlation filter is correlated
with the first row of the gram matrix, $\boldsymbol{k^{xz^{'}}}$, which
contains the similarity values between the learned feature template
$\boldsymbol{x}$ and the new test template $\boldsymbol{z}$. This can be
formulated as
\begin{equation}
\boldsymbol{r(z)} = F^{-1}(\boldsymbol{\hat{k}^{xz^{'}}} \odot \boldsymbol{\hat{\alpha}})
\end{equation}
where $\boldsymbol{r}$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features in tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activation of the first and
second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to increased translational invariance in this
layer. \cite{ma2015hierarchical} proposed a KCF tracker integrating
features with higher abstraction capacity.  Their method first employs
the third convolutional layer features to estimate the response
map. In the next stage, the KCF, concentrating on the second
convolutional layer features, is run to update transition. The third
KCF then works on the transition given by the previous KCF and learns
the first convolutional layer features to update the transition. This
coarse-to-fine translation estimation accommodates different levels of
abstractions of the object. However, it runs multiple KCFs in a
sequential fashion, increasing the run-time complexity. For this
reason, we follow an approach similar to
\cite{danelljan2015convolutional}, in order to embed deep features in
     {\it E}nKCF. Our {\it E}nKCF algorithm enables us to exploit
     different level of feature encodings with different KCFs. The
     translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at
     least twice bigger area than the scale filter, $R_{s}$. Given
     this, we can assign deeper feature encodings to $R_{s}$ as it
     learns less spatial information than $R_{t}^{L}$ and
     $R_{t}^{S}$. Thus we assign the activation of the fourth
     convolutional layer features ($26\times26\times128$) to $R_{s}$
     whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activation
     of the second layer features ($109\times109\times64$). Figure
     \ref{fig:Filters_CNN} illustrates this feature
     assignment. Additionally, we assign the second convolutional
     layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and
     compare this setting (\textit{conv222-VGG}) to
     \textit{conv224-VGG}. The conv222 setting stands for the
     assignment of the activation of $2^{th}$ convolutional layer
     features of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We
     use the VGGNet since it provides higher spatial resolution at the
     first several layers than AlexNet \cite{krizhevsky2012imagenet}.

@@

\textbf{Particle Filter for Smoothing Transition among KCFs} As
explained earlier, the {\it E}nKCF updates the target's scale at every
other $k$ frames. Although the strategy of updating every other $k$th
frames will result in an optimal run-time performance, this may lead
drifts at the later frames. To prevent such potential drifts, we
developed a Bayes filter that incorporates a target's motion to smooth
any intermediate outputs from individual KCFs. In particular, we use a
particle filter to estimate the target's image coordinate based on the
{\it E}nKCF's outputs. The state in this paper, $\boldsymbol{X_{t}}$,
represents the target's pixel coordinates and its velocity,
$\boldsymbol{X_{t}} = \lbrace x, y, v_{x}, v_{y} \rbrace$, where $x$
and $y$ are the pixel coordinates of the target's centroid, $v_x$ and
$v_y$ are the velocities estimated along the $x$-axis and
$y$-axis. The particle filter predicts, using a constant velocity
motion model, the target's next state by generating a predefined
number of particles. Then it uses the confidence maps of {\it E}nKCF
as observation to update its state. The particle weight is computed
as, $w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{M}
\boldsymbol{y_{R}}(x_{t}-i,y_{t}-j)$, where $w_{p}$ is the weight of
the particle $p$ at time $t$, $\boldsymbol{y_{R}}$ is the response map
from one of the KCFs, and $N$ and $M$ denote the number of rows and
columns of the confidence map.

@@

\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.60cm]{./figures/pr_deep.eps}
\includegraphics[width=3.70cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it fHoG} + {\it color-naming})
  performance with Deep{\it E}nKCF on the UAV123 dataset. The frame
  rate of the Deep{\it E}nKCF (conv224) was, on average, 30.74 fps and
  the conv222 setting was 35.23 fps on a CPU.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}
